---
title: "Haplotype Reconstruction with STITCH-Imputed Genotypes"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    code_folding: hide
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(qtl2)
library(qtl2fst)
library(tidyverse)
library(workflowr)
library(ggplot2)
```

# Overview

The goal of this preliminary analysis was to determine whether STITCH: 1) could provide us useful information and 2) whether this information could be translated or retrofitted for haplotype reconstruction in multiparent crosses

We built a Nextflow pipeline, [stitch-nf](https://github.com/TheJacksonLaboratory/stitch-nf), from the foundation of the NGS OPS WGS pipeline that runs STITCH on mouse samples that were submitted for low-coverage WGS. At the end of this pipeline, we extract 1) imputed sample genotypes and 2) prior probabilities for ancestral genotypes of latent haplotypes used for genotype imputation. These data can be conceptualized as "founder genotypes"

# Four-way Cross ddRADseq Test Samples

## Writing control file

```{r 4WC stitch control file}
# Establish chromosome vector
chr <- c(1:19)

# read in covariate file
metadata <- readr::read_csv(file = "data/4WC_covar.csv", 
                            col_types = c(sample = "c",
                                          generation = "n",
                                          Sex = "c"), 
                            show_col_types = T)

# match sample names to what is encoded in genotype files
geno_header <- c(as.character(readr::read_csv(file = "data/STITCH_data/4WC_ddRADseq/geno1.csv", 
                                              col_names = F, skip = 3, n_max = 1)))[-1]
new_sampleID <- c()
for(i in 1:length(metadata$SampleID)){
  sample_index <- grep(geno_header, pattern = gsub(metadata$SampleID[i], 
                                                   pattern = "-",
                                                   replacement = "."))
  new_sampleID[i] <- geno_header[sample_index]
}

# Write updated metadata file
updated_4WC_metadata <- metadata %>%
  dplyr::mutate(newSampID = new_sampleID) %>%
  dplyr::select(-SampleID,-Sex) %>%
  dplyr::select(newSampID, everything()) %>%
  dplyr::rename(SampleID = newSampID)
write.csv(updated_4WC_metadata, file = "data/STITCH_data/4WC_ddRADseq/4WC_ddRADseq_crossinfo.csv", quote = F, row.names = F)

# Write updated metadata file
sex_4WC <- metadata %>%
  dplyr::mutate(newSampID = new_sampleID) %>%
  dplyr::select(newSampID, Sex) %>%
  dplyr::rename(SampleID = newSampID) 
write.csv(sex_4WC, file = "data/STITCH_data/4WC_ddRADseq/sex_4WC.csv", quote = F, row.names = F)

# Write control file
qtl2::write_control_file(output_file = "data/STITCH_data/4WC_ddRADseq/4WC_ddRADseq.json",
                         crosstype="genail4",
                         description="4WC_ddRADseq",
                         founder_geno_file=paste0("foundergeno", chr, ".csv"), 
                         founder_geno_transposed=TRUE,
                         gmap_file=paste0("gmap", chr, ".csv"),
                         pmap_file=paste0("pmap", chr, ".csv"),
                         geno_file=paste0("geno", chr, ".csv"),
                         geno_transposed = TRUE,
                         geno_codes=list(A=1, H=2, B=3), 
                         sex_file = "sex_4WC.csv",
                         sex_codes=list(F="Female", M="Male"),
                         # crossinfo_covar=c("Generation","A","B","C","D"), 
                         crossinfo_file = "4WC_ddRADseq_crossinfo.csv",
                         overwrite = T)

```

We load in the cross object, and determined the number of markers that are missing data in each sample. These data are from a small test run of ddRADseq libraries prepped by Lydia Wooldridge and the Dumont Lab.

## Calculating missing genotypes

```{r missing genotypes 4WC}
# Load in the cross object
ddRADseq_4WC <- qtl2::read_cross2("data/STITCH_data/4WC_ddRADseq/4WC_ddRADseq.json")

# Also loading in the cross object from GigaMUGA genotypes
load("data/4WC_cross.RData")

# Drop null markers
ddRADseq_4WC <- qtl2::drop_nullmarkers(ddRADseq_4WC)

# Reordering genotypes so that most common allele in founders is first
for(chr in seq_along(ddRADseq_4WC$founder_geno)) {
  fg <- ddRADseq_4WC$founder_geno[[chr]]
  g <- ddRADseq_4WC$geno[[chr]]
  f1 <- colSums(fg==1)/colSums(fg != 0)
  
  fg[fg==0] <- NA
  g[g==0] <- NA
  
  fg[,f1 < 0.5] <- 4 - fg[,f1 < 0.5]
  g[,f1 < 0.5]  <- 4 - g[,f1 < 0.5]
  
  fg[is.na(fg)] <- 0
  g[is.na(g)] <- 0
  
  ddRADseq_4WC$founder_geno[[chr]] <- fg
  ddRADseq_4WC$geno[[chr]] <- g
}

# Calculate the percent of missing genotypes per sample
percent_missing <- qtl2::n_missing(ddRADseq_4WC, "ind", "prop")*100
missing_genos_df <- data.frame(names(percent_missing), percent_missing) %>%
  `colnames<-`(c("sample","percent_missing"))

# Plot missing genotypes per sample
missing_genos_plot <- ggplot(data = missing_genos_df, mapping = aes(x = reorder(sample, percent_missing),
                                                                    y = percent_missing)) +
  theme_bw() +
  geom_point(shape = 21) +
  labs(title = "4WC Missing Genotypes") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
plotly::ggplotly(missing_genos_plot)

percent_missing_cutoff <- 10
```

`r nrow(missing_genos_df %>% dplyr::filter(percent_missing > percent_missing_cutoff))` 4WC sample(s) is/are missing data for greater than `r percent_missing_cutoff`% of markers.

## Sample duplicates

We next calculated whether, based on genotype information alone, samples appear to be duplicates. We estimated from GigaMUGA data that there are probably no duplicate samples.

```{r sample duplicates 4WC}
# Determine if any samples are duplicates based on genetic similarity
cg <- qtl2::compare_geno(ddRADseq_4WC, cores=0)
qtl2::plot_compare_geno(x = cg, rug = T, main = "4WC - ddRADseq Data")
```

From the above plot, it would seem that the genotyping can't distinguish certain samples from each other.

```{r sample duplicates for GM}
cgGM <- qtl2::compare_geno(X4WC_cross, cores=0)
qtl2::plot_compare_geno(x = cgGM, rug = T, main = "4WC - GigaMUGA Data")
```

These mice are F2/F3 individuals, so we expect that they retain a good deal of relatedness. We would hypothesize that due to the lower coverage of the ddRADseq genotyping that we miss areas of the genome that would distinguish individuals from each other.

## Haplotype reconstruction

```{r haplotype reconstruction for ddRADseq 4WC, fig.height=9}
# Insert pseudomarkers
map <- qtl2::insert_pseudomarkers(ddRADseq_4WC$gmap, step = 1)

# Calculate genotype probs
dir.create("results/4WC_ddRADseq_pr")
fpr <- suppressWarnings(qtl2fst::calc_genoprob_fst(cross = ddRADseq_4WC, 
                                                   map = map,
                                                   fbase = "pr",
                                                   fdir = "results/4WC_ddRADseq_pr",
                                                   error_prob=0.002, 
                                                   overwrite=TRUE,cores = parallel::detectCores()))

# Make viterbi
m <- maxmarg(fpr, minprob=0.5)

# Phase genotypes
ph <- qtl2::guess_phase(cross = ddRADseq_4WC, geno = m)

# Write Plots
X4WCcolors <- c(qtl2::CCcolors[6],
  "#5ADBFF",
  "#153B50",
  qtl2::CCcolors[7])
names(X4WCcolors)[2:3] <- c("POHN","GOR")
for(i in 1:nrow(ddRADseq_4WC$cross_info)){
  png(file=paste0("output/plot_onegeno_",rownames(ddRADseq_4WC$cross_info)[i],".png"))
  qtl2::plot_onegeno(geno = ph, 
                     map = map,
                     ind = i, 
                     col = X4WCcolors) # add legends here
  legend(17, 85, 
         legend=c("A", "B", "C", "D"),
         fill=X4WCcolors, cex=0.8)
  dev.off()
}
```

Below are example chromosome paintings of haplotype reconstructions from 4WC ddRADseq samples compared to the same individiuals genotyped with GigaMUGA.

```{r haplotype plots 4WC}
# GigaMUGA haplotypes
load("data/4WC_genoprobs.RData")
gm_m <- maxmarg(pr, minprob=0.5)
gm_ph <- qtl2::guess_phase(cross = X4WC_cross, geno = gm_m)
gm_map <- qtl2::insert_pseudomarkers(X4WC_cross$gmap, step = 1)

# Example plots
indivs <- sample(seq(1:nrow(ddRADseq_4WC$cross_info)), size = 5, replace = F)

# ddRADseq
plot_indiv <- rownames(ddRADseq_4WC$cross_info)[indivs[1]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = X4WCcolors,
                   main = plot_indiv) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)
# DO
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(X4WC_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = X4WCcolors,
                   main = rownames(X4WC_cross$cross_info)[do_sample_index]) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)


plot_indiv <- rownames(ddRADseq_4WC$cross_info)[indivs[2]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = X4WCcolors,
                   main = plot_indiv) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(X4WC_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = X4WCcolors,
                   main = rownames(X4WC_cross$cross_info)[do_sample_index]) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)


plot_indiv <- rownames(ddRADseq_4WC$cross_info)[indivs[3]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = X4WCcolors,
                   main = plot_indiv) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(X4WC_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = X4WCcolors,
                   main = rownames(X4WC_cross$cross_info)[do_sample_index]) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)


plot_indiv <- rownames(ddRADseq_4WC$cross_info)[indivs[4]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = X4WCcolors,
                   main = plot_indiv) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(X4WC_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = X4WCcolors,
                   main = rownames(X4WC_cross$cross_info)[do_sample_index]) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)

plot_indiv <- rownames(ddRADseq_4WC$cross_info)[indivs[5]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = X4WCcolors,
                   main = plot_indiv) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(X4WC_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = X4WCcolors,
                   main = rownames(X4WC_cross$cross_info)[do_sample_index]) # add legends here
legend(17, 85, legend=c("A", "B", "C", "D"), fill=X4WCcolors, cex=0.8)

```

A few things can be observed from these plots. First, the ddRADseq haplotypes reflect complete homozygosity, which is not possible for these mice. This is could be due to low coverage in these test runs; a lack of sequencing depth across sites will result in not enough data to call heterozygous sites confidently. The degree of missing genotypes across samples reflects this lack of depth.

Second, many of the haplotype identities are discordant between the GigaMUGA and ddRADseq samples at the same genomic sites. This could reflect the fact that the same ancestral haplotype that STITCH denotes as "A" is not the same as the haplotype derived from qtl2. We could work around this by supplying a smaller set of well-curated consensus genotypes. We haven't tested whether including these data improve the functionality of STITCH for our purposes.

# Diversity Outbred ddRADseq Test Samples

## Writing control file

There are a handful of DO samples in the metadata which were not sequenced as a test run. Those samples throw the "sample from metadata not sequenced" error observed below.

```{r DO stitch control file}
# Establish chromosome vector
chr <- c(1,3:19)

# read in covariate file
metadata <- readr::read_csv(file = "data/DO_covar.csv", 
                            col_types = c(sample = "c",
                                          Sex = "c",
                                          generation = "n"), 
                            show_col_types = T)

# match sample names to what is encoded in genotype files
geno_header <- c(as.character(readr::read_csv(file = "data/STITCH_data/DO_ddRADseq/geno1.csv", 
                                              col_names = F, skip = 3, n_max = 1)))[-1]
new_sampleID <- c()
for(i in 1:length(metadata$SampleID)){
  sample_index <- grep(geno_header, pattern = gsub(metadata$SampleID[i], 
                                                   pattern = "-",
                                                   replacement = "."))
  if(length(sample_index) == 0){
    print(paste("sample from metadata not sequenced:", metadata$SampleID[i]))
    new_sampleID[i] <- NA
  } else {
    new_sampleID[i] <- geno_header[sample_index]
  }
  
}

# Write updated metadata file
updated_DO_metadata <- metadata %>%
  dplyr::mutate(newSampID = new_sampleID) %>%
  dplyr::select(-SampleID) %>%
  dplyr::select(newSampID, everything()) %>%
  dplyr::rename(SampleID = newSampID) %>%
  dplyr::filter(!is.na(SampleID))
write.csv(updated_DO_metadata, file = "data/STITCH_data/DO_ddRADseq/DO_ddRADseq_crossinfo.csv", quote = F, row.names = F)

# Write control file
qtl2::write_control_file(output_file = "data/STITCH_data/DO_ddRADseq/DO_ddRADseq.json",
                         crosstype="do",
                         description="DO_ddRADseq",
                         founder_geno_file=paste0("foundergeno", chr, ".csv"), 
                         founder_geno_transposed=TRUE,
                         gmap_file=paste0("gmap", chr, ".csv"),
                         pmap_file=paste0("pmap", chr, ".csv"),
                         geno_file=paste0("geno", chr, ".csv"),
                         geno_transposed = TRUE,
                         geno_codes=list(A=1, H=2, B=3), 
                         sex_covar = "Sex",
                         sex_codes=list(F="Female", M="Male"), 
                         covar_file = "DO_ddRADseq_crossinfo.csv",
                         crossinfo_covar="Generation",
                         overwrite = T)
```

## Calculating missing genotypes

```{r missing genotypes DO}
# Load in the cross object
ddRADseq_DO <- qtl2::read_cross2("data/STITCH_data/DO_ddRADseq/DO_ddRADseq.json")

# Also loading in the cross object from GigaMUGA genotypes
load("data/DO_cross.RData")

# Drop null markers
ddRADseq_DO <- qtl2::drop_nullmarkers(ddRADseq_DO)

# Reordering genotypes so that most common allele in founders is first
for(chr in seq_along(ddRADseq_DO$founder_geno)) {
  fg <- ddRADseq_DO$founder_geno[[chr]]
  g <- ddRADseq_DO$geno[[chr]]
  f1 <- colSums(fg==1)/colSums(fg != 0)
  
  fg[fg==0] <- NA
  g[g==0] <- NA
  
  fg[,f1 < 0.5] <- 4 - fg[,f1 < 0.5]
  g[,f1 < 0.5]  <- 4 - g[,f1 < 0.5]
  
  fg[is.na(fg)] <- 0
  g[is.na(g)] <- 0
  
  ddRADseq_DO$founder_geno[[chr]] <- fg
  ddRADseq_DO$geno[[chr]] <- g
}

# Calculate the percent of missing genotypes per sample
percent_missing <- qtl2::n_missing(ddRADseq_DO, "ind", "prop")*100
missing_genos_df <- data.frame(names(percent_missing), percent_missing) %>%
  `colnames<-`(c("sample","percent_missing"))

# Plot missing genotypes per sample
missing_genos_plot <- ggplot(data = missing_genos_df, mapping = aes(x = reorder(sample, percent_missing),
                                                                    y = percent_missing)) +
  theme_bw() +
  geom_point(shape = 21) +
  labs(title = "DO Missing Genotypes") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
plotly::ggplotly(missing_genos_plot)

percent_missing_cutoff <- 10
```

`r nrow(missing_genos_df %>% dplyr::filter(percent_missing > percent_missing_cutoff))` DO sample(s) is/are missing data for greater than `r percent_missing_cutoff`% of markers.

## Sample Duplicates

```{r sample duplicates DO}
# Determine if any samples are duplicates based on genetic similarity
cg <- qtl2::compare_geno(ddRADseq_DO, cores=0)
qtl2::plot_compare_geno(x = cg, rug = T, main = "DO - ddRADseq Data")
```

There are many "duplicates" among the DO ddRADseq samples as well. Compared to the DO GigaMUGA samples:

```{r sample duplicates DO GM}
cgGM <- qtl2::compare_geno(DO_cross, cores=0)
qtl2::plot_compare_geno(x = cgGM, rug = T, main = "DO - GigaMUGA Data")
```

## Haplotype Reconstruction

```{r haplotype reconstruction for ddRADseq DO, fig.height=9}
# Insert pseudomarkers
map <- qtl2::insert_pseudomarkers(ddRADseq_DO$gmap, step = 1)

# Calculate genotype probs
dir.create("results/DO_ddRADseq_pr")
fpr <- suppressWarnings(qtl2fst::calc_genoprob_fst(cross = ddRADseq_DO, 
                                                   map = map,
                                                   fbase = "pr",
                                                   fdir = "results/DO_ddRADseq_pr",
                                                   error_prob=0.002, 
                                                   overwrite=TRUE,cores = parallel::detectCores()))

# Make viterbi
m <- maxmarg(fpr, minprob=0.5)

# Phase genotypes
ph <- qtl2::guess_phase(cross = ddRADseq_DO, geno = m)

# Write Plots
for(i in 1:nrow(ddRADseq_DO$cross_info)){
  png(file=paste0("output/plot_onegeno_",rownames(ddRADseq_DO$cross_info)[i],".png"))
  qtl2::plot_onegeno(geno = ph, 
                     map = map,
                     ind = i, 
                     col = c(qtl2::CCcolors)) # add legends here
  legend(16, 70, 
         legend=c("A", "B", "C", "D",
                  "E", "F", "G", "H"),
         fill=c(qtl2::CCcolors), cex=0.8)
  dev.off()
}
```

Below are example chromosome paintings of haplotype reconstructions from DO ddRADseq samples compared to the same individuals genotyped with GigaMUGA.

```{r haplotype plots DO}
# GigaMUGA haplotypes
load("data/DO_genoprobs.RData")
gm_m <- maxmarg(pr, minprob=0.5)
gm_ph <- qtl2::guess_phase(cross = DO_cross, geno = gm_m)
gm_map <- qtl2::insert_pseudomarkers(DO_cross$gmap, step = 1)

# Example plots
indivs <- sample(seq(1:nrow(ddRADseq_DO$cross_info)), size = 5, replace = F)

# ddRADseq
plot_indiv <- rownames(ddRADseq_DO$cross_info)[indivs[1]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = c(qtl2::CCcolors),
                   main = plot_indiv) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)
# DO
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(DO_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = c(qtl2::CCcolors),
                   main = rownames(DO_cross$cross_info)[do_sample_index]) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)


plot_indiv <- rownames(ddRADseq_DO$cross_info)[indivs[2]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = c(qtl2::CCcolors),
                   main = plot_indiv) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(DO_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = c(qtl2::CCcolors),
                   main = rownames(DO_cross$cross_info)[do_sample_index]) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)


plot_indiv <- rownames(ddRADseq_DO$cross_info)[indivs[3]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = c(qtl2::CCcolors),
                   main = plot_indiv) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(DO_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = c(qtl2::CCcolors),
                   main = rownames(DO_cross$cross_info)[do_sample_index]) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)


plot_indiv <- rownames(ddRADseq_DO$cross_info)[indivs[4]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = c(qtl2::CCcolors),
                   main = plot_indiv) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(DO_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = c(qtl2::CCcolors),
                   main = rownames(DO_cross$cross_info)[do_sample_index]) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)


plot_indiv <- rownames(ddRADseq_DO$cross_info)[indivs[5]]
qtl2::plot_onegeno(geno = ph, 
                   map = map,
                   ind = plot_indiv, 
                   col = c(qtl2::CCcolors),
                   main = plot_indiv) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)
do_sample_index  <- grep(pattern = gsub(strsplit(plot_indiv, split = "_")[[1]][1], 
                                        pattern = "ddRADseq.",
                                        replacement = ""),
                         x = gsub(rownames(DO_cross$cross_info), 
                                  pattern = "-", 
                                  replacement = "."))
qtl2::plot_onegeno(geno = gm_ph, 
                   map = gm_map,
                   ind = do_sample_index, 
                   col = c(qtl2::CCcolors),
                   main = rownames(DO_cross$cross_info)[do_sample_index]) # add legends here
legend(16, 65, legend=LETTERS[1:8], fill=c(qtl2::CCcolors), cex=0.8)

```
